Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-11-30 paperIEEE.tex
Omegalib section
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@65 db7c848b-7755-4df2-b763-8796797afa52

\FIXME{add text}

>>>>

Omegalib \cite{Omegalib} is a software framework built on top of Equalizer that
facilitates application development for hybrid reality environments such as the
Cave 2. Hybrid reality enviroments aim to create a seamless 2D/3D environment
that supports both information-rich analysis (traditionally done on tiled
display wall) as well as virtual reality simulation exploration (traditionally
done in VR systems) at a resolution matching human visual acuity. Omegalib
supports dynamic reconfigurability of the display environment, so that areas of
the display can be interactively allocated to 2D or 3D workspaces as needed. It
makes it possible to have multiple immersive applications running on a
cluster-controlled display system, have different input sources dynamically
routed to applications, and have rendering results optionally redirected to a
distributed compositing manager. Omegalib supports pluggable front-ends, to
simplify the integration of third-party libraries like OpenGL, OpenSceneGraph,
and the Visualization Toolkit (VTK).
